---
title: "R Notebook"
output: html_notebook
---

```{r}
# Carregar pacotes necessários
library(survival)
library(ggplot2)
library(survminer)
library(dplyr)

# Carregar o conjunto de dados cancer
data(cancer, package="survival")

# Limpeza dos dados: remover observações com dados ausentes
cancer <- cancer %>%
  na.omit()

# Visualizar os dados
head(cancer)
```
## Data description:

- inst: Institution code
- time: Survival time in days
- status: censoring status 1=censored, 2=dead
- age: Age in years
- sex: Male=1 Female=2
- ph.ecog: ECOG performance score as rated by the physician. 0=asymptomatic, 1= symptomatic but completely ambulatorph.karno: Karnofsky performance score (bad=0-good=100) rated by physician
- pat.karno: Karnofsky performance score as rated by patient
- meal.cal: Calories consumed at meals
- wt.loss: Weight loss in last six months (pounds)

## Análise descritiva
```{r}
summary(cancer)
```

## Ajustar o modelo de Weibull
```{r}
weibull_model <- survreg(Surv(time, status) ~ age + sex + meal.cal, data = cancer, dist = "weibull")
```
